Workflow and Software Documentation

### 2013-07-09 Workflow.Rnw

\section{Ternary Plots}
\begin{enumerate}
\item
Plots of distributions of coefficients for the Cobb-Douglas 
with energy model can be made with \function{triPlot()} in 
file \texttt{Graphics.R}.
<<>>=
source("Graphics.R")
resData <- loadAllResampleData(modelType="cde", energyType="Q")
triPlot(subset(resData, method!="orig"), 
        gamma, alpha, beta,
        labels=c("gamma", "alpha", "beta"),
        n.grid=5,  aes_string="color=lambda", 
        size=3, alpha=.5 ) + 
     geom_point(data=subset(resData, method=="orig"), 
                color="red", alpha=1, size=3) +
     facet_wrap( ~ countryAbbrev )
@
Eventually, we can build a wrapper that loads the data and builds the plot with our favorite settings.
\end{enumerate}

>>>>

\section{Ternary Plots}
\begin{enumerate}
\item
Plots of distributions of coefficients for the Cobb-Douglas 
with energy model can be made with \function{triPlot()} in 
file \texttt{Graphics.R}.  (Goofy labels here just to demonstrate what is possible.)
<<>>=
source("Graphics.R")
resData <- loadAllResampleData(modelType="cde", energyType="Q")
triPlot(subset(resData, method!="orig"), 
        gamma, alpha, beta,
        labels=c("gamma[1]", "alpha[2]", "sqrt(beta[3])"),
        n.grid=5,  aes_string="color=lambda", 
        size=1.7, alpha=.5 ) + 
     geom_point(data=subset(resData, method=="orig"), 
                color="red", alpha=1, size=3) +
     facet_wrap( ~ countryAbbrev ) +
     scale_colour_gradient(expression(lambda), high="navy", low="skyblue")
@
Eventually, we can build a wrapper that loads the data and builds the plot with our favorite settings.
\end{enumerate}
